\documentclass[12pt]{report}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}               
\usepackage{setspace}                
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{fullpage}

\newenvironment{myitemize}
{ \begin{itemize}
    \setlength{\itemsep}{5pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  } 

\begin{document}
\setlength\parindent{0pt}

\begin{center}
\large
Syllabus for STAT 310: Statistics for Social Sciences\\
\large
Spring 2021\\   
\end{center}
\vspace{10pt}

\normalsize
\textbf{Instructor:} Dr.~Eric Fox\\ 
Office: SC-N 303A\\ 
Email: \url{eric.fox@csueastbay.edu}\\
%Phone: 510-885-4905 \\

\textbf{Lecture:} Tu/Th 3:15-4:55 over Zoom\\

\textbf{Office Hours:} Tu/Th 1-2PM and Wed 2-4PM, or by appointment\\
Zoom link: \url{https://csueb.zoom.us/j/502694714}\\

\textbf{Website:} Course materials will be posted on Blackboard.\\ 

\textbf{Textbook}:  Diez, D., Barr, C. and Cetinkaya-Rundel M. \emph{OpenIntro Statistics}, 4th Edition, 2019. [Free PDF: \url{https://www.openintro.org/stat/textbook.php}]\\

\textbf{Software}:\\ 
R, can be downloaded here \url{https://www.r-project.org/}\\
RStudio, can be downloaded here \url{https://www.rstudio.com/}\\ 

\textbf{Course Topics}:  This course will provide an introduction to statistics with a focus on applications to social sciences. Topics include exploratory data analysis, statistical inference, and linear regression.  Computer labs will provide training in the use of the statistical programming language R.
\begin{myitemize}
\item Data collection: sampling designs and experimental studies
\item Descriptive statistics and data visualization
\item Normal distribution
\item Sampling distributions 
\item Confidence intervals 
\item Hypothesis testing
\item Linear regression and correlation\\
\end{myitemize}

%\newpage

\textbf{Grading:}
\begin{myitemize}
\item 10\% Homework
\item 15\% Computer Labs 
\item 75\% Three Exams (take-home, 25\% each)\\
\end{myitemize}

%\newpage

\textbf{Policy on Late Assignments and Exams:}  Late homework will generally not be accepted.  However, your lowest scoring homework and lab assignment will be dropped.  I may agree to extensions on due dates if you are experiencing an emergency or illness.\\

\textbf{Student Learning Outcomes:}  Upon successful completion of this course, students should be able to:
\begin{myitemize}
\item Apply statistical methodologies, including (a) summary statistics and graphical displays, (b) hypothesis testing and confidence intervals, and (c) linear regression and correlation.
\item Understand basic theory underlying these methodologies. 
\item Use R and RStudio to analyze data sets and implement statistical methods.
\item Communicate statistical concepts clearly and appropriately to others.\\ 
\end{myitemize}

\textbf{Technology Requirements:}  This course will use the web conferencing software Zoom.  To participate you will need a stable internet connection,  and a laptop or desktop computer equipped with a webcam, microphone, and speakers.  Please refer to the Zoom system requirements \href{https://support.zoom.us/hc/en-us/articles/201362023-System-requirements-for-Windows-macOS-and-Linux}{here}.\\

\textbf{Course Policies and Zoom Etiquette}:
\begin{myitemize}
\item All lectures will be delivered live during the scheduled class time, and attendance is highly recommended.  Recordings of the sessions will be posted on Blackboard for students that cannot attend or have connectivity issues.   
\item Make sure that your audio is muted upon entry into the class.
\item You may ask questions by using the chat function or by unmuting yourself.  Please try to not disrupt the instructor or other students.\\
\end{myitemize}

\textbf{Common Syllabus Items:}  Items such as policies on academic dishonesty, disability, and handling emergency situations can be found under ``University Policies" on Blackboard.








\end{document}